Time Series Bootstrapping For Solar Current

### 2021-12-08 deliverables/paper.Rmd
Added figure-saving to paper and figures to presentation

@@

#' Plot a timeseries of a single variable
#'
#' @param df A dataframe containing `variable`
#' @param variable A string referring to a column of `df`
#' @param n_days The number of days (starting from the
#'    beginning of the data) to plot
#' @return A ggplot object of a timeseries of `variable` for `n_days` days
time_series_of_var <- function(df, variable, n_days) {
  ret_plot <- df %>%
    mutate(date = lubridate::make_datetime(Year, Month, Day, Hour, Minute)) %>%
    head(24 * n_days) %>%
    ggplot() +
    geom_line(aes_string(x = "date", y = variable)) +
    theme_bw()
  return(ret_plot)
}

time_series_of_var(df, "GHI", 6)
time_series_of_var(df, "current_out", 6)
```

@@

#' Plot the values of `variable` at each hour of the day
#'
#' @param df A dataframe containing `variable`
#' @param variable A string referring to a column of `df`
#' @return A ggplot object of a boxplot of `variable` segmented by hour
hour_plot_of_var <- function(df, variable) {
  df$Hour <- as.factor(df$Hour)
  ret_plot <- df %>%
    ggplot() +
    geom_boxplot(aes_string(x = "Hour", y = variable)) +
    xlab("Hour (0-23)") +
    ylab(paste("Distribution of", variable)) +
    theme_bw()
  return(ret_plot)
}

hour_plot_of_var(df, "GHI")
hour_plot_of_var(df, "current_out")
```

>>>>

```{r plot-pres-func}
make_plot_for_pres <- function(plot) {
  ret_plot <- plot +
  theme(text=element_text(size=21))
  return(ret_plot)
}
```

@@

#' Plot a timeseries of a single variable
#'
#' @param df A dataframe containing `variable`
#' @param variable A string referring to a column of `df`
#' @param var_name The human-readable name of `variable`, for labelling
#' @param n_days The number of days (starting from the
#'    beginning of the data) to plot
#' @return A ggplot object of a timeseries of `variable` for `n_days` days
time_series_of_var <- function(df, variable, var_name, n_days) {
  ret_plot <- df %>%
    mutate(date = lubridate::make_datetime(Year, Month, Day, Hour, Minute)) %>%
    head(24 * n_days) %>%
    ggplot() +
    geom_line(aes_string(x = "date", y = variable)) +
    xlab("Date") +
    ylab(var_name) +
    theme_bw()
  return(ret_plot)
}

time_series_ghi <- time_series_of_var(df, "GHI", "GHI", 6)
time_series_current <- time_series_of_var(df, "current_out", "Output current", 6)
ggsave("./images/time_series_ghi.png", make_plot_for_pres(time_series_ghi))
ggsave("./images/time_series_current.png", make_plot_for_pres(time_series_current))
```

@@

#' Plot the values of `variable` at each hour of the day
#'
#' @param df A dataframe containing `variable`
#' @param variable A string referring to a column of `df`
#' @param var_name The human-readable name of `variable`, for labelling
#' @return A ggplot object of a boxplot of `variable` segmented by hour
hour_plot_of_var <- function(df, variable, var_name) {
  df$Hour <- as.factor(df$Hour)
  ret_plot <- df %>%
    ggplot() +
    geom_boxplot(aes_string(x = "Hour", y = variable)) +
    xlab("Hour (0-23)") +
    ylab(paste("Distribution of", var_name)) +
    theme_bw()
  return(ret_plot)
}

hour_plot_ghi <- hour_plot_of_var(df, "GHI", "GHI")
hour_plot_current <- hour_plot_of_var(df, "current_out", "output current")
ggsave("./images/hour_plot_ghi.png", make_plot_for_pres(hour_plot_ghi))
ggsave("./images/hour_plot_current.png", make_plot_for_pres(hour_plot_current))
```

### 2021-12-08 deliverables/presentation.Rmd
Fixed preprocessing order
Added figure-saving to paper and figures to presentation

@@

1. Astronomical adjustment: GHI $\rightarrow$ effective irradiance
1. Power processor: Effective irradiance + voltage $\rightarrow$ current 
1. PV Module: Effective irradiance $\rightarrow$ current

@@

ADD FIGURES

>>>>

::: columns
:::: column
![](./images/time_series_ghi.png)
::::
:::: column
![](./images/hour_plot_ghi.png)
::::
:::

@@

1. Astronomical adjustment: GHI $\rightarrow$ effective irradiance
1. PV Module: Effective irradiance + voltage $\rightarrow$ current 
1. Power processor: Effective irradiance $\rightarrow$ current

@@

::: columns
:::: column
![](./images/time_series_ghi.png)
::::
:::: column
![](./images/time_series_current.png)
::::
:::

# Postprocessed data, cont.

::: columns
:::: column
![](./images/hour_plot_ghi.png)
::::
:::: column
![](./images/hour_plot_current.png)
::::
:::
